### 2018-06-18 Thesis/Parts/Abstract/Abstract.tex
Background feedback added

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Abstract}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on generic text, which do not contain the complexity of in-domain knowledge, such as rare domain specific words. This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017. The data shows that the word embeddings only perform better than TF-IDF, which was chosen as a traditional alternative, when the ranking is done on titles. The best ranking result is obtained through a TF-IDF with a vocabulary size of 10.000 applied on the abstracts, resulting in a median rank of 14, while the pure word embeddings result in a median rank of 23. This shows that word embeddings, although useful, are not unchallenged by older techniques.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Abstract}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on generic text, which do not contain the characteristics of in-domain knowledge, such as rare domain specific words. This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017. The data shows that the word embeddings only perform better than TF-IDF, which was chosen as a traditional alternative, when the ranking is done on titles. The best ranking result is obtained through a TF-IDF with a vocabulary size of 10.000 applied on the abstracts, resulting in a median rank of 14, while the pure word embeddings result in a median rank of 23. This shows that word embeddings, although useful, are not unchallenged by older techniques.
\end{document}

### 2018-06-18 Thesis/Parts/Background/Background.tex
Background feedback added

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Introduction and Background}
\subheader{Information retrieval}
Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. The most practical example of this is a search engine. Given one or more search words the search engine will attempt to find relevant information. For example, a Google search on "Information Retrieval" (initial piece of information) will give you a list of results (relevant information). To be able to do this, the computer (search engine) must know which texts are related. To achieve this, multiple techniques can be used, such as TF-IDF, Word2Vec, Paragraph Vectors and GloVe. These techiques can be divided into two categories, ones that use a neural network and ones that do not.
\subheader{Neural Network}
Neural Networks are computational structures, based on vector and/or matrix calculations. They can be applied to many different tasks, but need to be trained for each task. This training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result. Which is the result that is as close as possible to the given output for different input and output sets.
In some IR techniques, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it. For example, given the sentence\\
\begin{center}
\textit{"The search engine searches for relevant information"}
\end{center}
the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information). This trained matrix (vector per word) now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts. Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
%The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
\subheader{Embedding}
The created vector for a word is referred to as a word embedding. An embedding is a distributed, numerical representation of a text which can capture both the semantic and syntactic information\cite{mikolov2013distributed}. In the case of a word embedding, the embedding represents the word. The advantage of the machine learning models that create these embeddings is that they do not need human interaction~\citet{lai2016generate}, they are so called "unsupervised learning algorithms". Once trained, the embeddings can be used to construct embeddings of larger texts. For example, a word embedding can be used to create a sentence, paragraph, document or corpus embedding. The usage of word embeddings have improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.

@@

\subsubheader{TF-IDF}
TF-IDF is an abbreviation for Term Frequency times Inverted Document Frequency. This method does not rely on a neural network and therefore does not require training. The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts. Both of which can be calculated in a variety of ways. The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
\end{jumpin}
As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", all embedding methods rely on the same hypothesis, words that occur in similar contexts have similar meanings. They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained is dominant over the corpus size.

\subheader{Validation methods}
The results produced by the techniques have to be validated to determine their quality (in usage). The quality of the results can be validated through, among others the F1 score and, for classification tasks, the rank of the correct category. The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization. These tasks can be designed to produce a score that gives an indication of the performance on a specific task. \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks. Embeddings that perform well on one task do not have to perform well on another task. As a result, the findings about performance of an embedding method are limited to the task on which they are tested, their results cannot be generalized to state that the embedding are overall "performing well". Validation tasks use either labelled or unlabelled data. Labelled data is data that is in some way marked, so that the correct answer can be derived from it, in contrast to unlabelled data. The validation tasks can also be diveded into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task. And Intrinsic evaluation, which directly test the relationships of the word embedding themselves. \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations, since the performance on downstream tasks is not consistent across tasks.

@@

Since the word embeddings are created form a given text, these embeddings are bound to the text. All meaning embedded in the word embedding is derived from the original text. Because of this, embeddings can be "Domain specific" meaning that it only knows words (or a specific word) in a certain context. This becomes most clear when faced with words that can have different meanings in different contexts. For this research we categorize the embedding in two categories, general embeddings and domain specific embeddings. The general embeddings are trained on a collection of texts that use common English and contains a wide variety of topics. The domain specific embeddings are trained on a collection of texts that uses uncommon English (i.e. domain specific terms) and/or is limited to a small amount of topics. Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics. On the other hand we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific, these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Introduction and Background}
\subheader{Information retrieval}
Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. The most practical example of this is a search engine. Given one or more search words the search engine will attempt to find relevant information. For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information). To be able to do this, the search engine must know which texts are related. This can be achieved with and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency. Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.

\subheader{Neural Network}
Neural Networks are computational structures, based on vector and/or matrix calculations. They can be applied to many different tasks, but need to be trained for each task. This training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result. Which is the result that is as close as possible to the given output for different input and output sets.
In some IR techniques, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it. For example, given the sentence\\
\begin{center}
\textit{"The search engine searches for relevant information"}
\end{center}
the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information). This trained matrix, a vector per word which is referred to as a word embedding, now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts. Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
%The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
\subheader{Embedding}
An embedding is a distributed, numerical representation of a text in a vector space\footnote{The vector space of separately trained word embeddings are not shared, since the trained vector dimensions are not fixed. This means that two separately trained word embeddings which have the same dimension do not share the same vector space.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}. In the case of a word embedding, the embedding represents the word. These embeddings are created using by machine learning models. These models create the embeddings without the need for human interaction~\cite{lai2016generate}, they are so called \textit{unsupervised learning algorithms}. Once trained, the embeddings can be used to construct embeddings for collections of texts. For example, a word embedding can be used to create a sentence, paragraph, document or corpus embedding. The usage of word embeddings have improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.

@@

\subsubheader{TF-IDF}
TF-IDF is an abbreviation for Term Frequency times Inverted Document Frequency. This method does not rely on a neural network and therefore does not require training. The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts. Both of which can be calculated in a variety of ways. The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences. These features are created by supplying the algorithm with the text it needs to "know". This text is then analysed on word occurrences on corpus and document and level, this results in a score per-word. This score can be converted to a feature vector, in which the indexes of these vector represent the words and the value is the TF-IDF score. The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size. If this is not applied, the size of the feature vector is equal to the amount of unique words in the corpus, also known as the (corpus) vocabulary. Some applications of this technique limit the amount of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence. This reduces the amount of storage needed when hashing is not applied. It furthermore reduces the amount of words which occur rarely. Due to the nature of TF-IDF these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.

\end{jumpin}
As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", all embedding methods rely on the same hypothesis, words that occur in similar contexts have similar meanings. They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained is dominant over the corpus size.

\subheader{Validation methods}
The results produced by the techniques have to be validated to determine their quality (in usage). The quality of the results can be validated through, among others the F1 score, which combines the precision score and the recall score in a single metric, and, for classification tasks, the rank of the correct category. The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization. These tasks can be designed to produce a score that gives an indication of the performance on a specific task. \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks. Embeddings that perform well on one task do not have to perform well on another task. As a result, the findings about performance of an embedding method are limited to the task on which they are tested, their results cannot be generalized to state that the embedding are overall "performing well". Validation tasks use either labelled or unlabelled data. Labelled data is data that is in some way marked, so that the correct answer can be derived from it, while this is not possible with unlabelled data. Labelled data enables the usage of unsupervised learning models, since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration. Unlabelled data on the other hand requires human interaction to give a score for the produced result. The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task. And Intrinsic evaluation, which directly test the relationships of the word embedding themselves. \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations, since the performance on downstream tasks is not consistent across tasks.

@@

Since the word embeddings are created form a given text, these embeddings are bound to the text. All meaning embedded in the word embedding is derived from the original text. Because of this, embeddings can be "Domain specific" meaning that it only knows words (or a specific word) in a certain context. This becomes most clear when faced with words that can have different meanings in different contexts. For this research we categorize the embedding in two categories, general embeddings and domain specific embeddings. The general embeddings are trained on a collection of texts that use common English and contains a wide variety of topics. The domain specific embeddings are trained on a collection of texts that uses uncommon English (i.e. domain specific terms) and/or is limited to a small amount of topics. Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics. On the other hand we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific, these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus. The domain specific texts can use the same word for unrelated topics, like clouds in computer science and meteorology.
